Secure Composition of Robust and Optimising Compilers

### 2023-07-12 popl/main.tex

So far, the paper explained how to relate an $\Ltms$ execution with a $\Ltrg$ execution.
The next question is therefore how to build the corresponding $\Ltms$ execution.
This is done using a standard secure compilation proof technique called trace-based backtranslation~\cite{abate2019jour,korashy2021capableptrs,patrignani2021rsc}, which can be used to build a context $\src{\library_{\ctx}}$ that behaves similar to $\trg{\library_{\ctx}}$.
% Since $\Ltms$ is statically typed, the context $\src{\library_{\ctx}}$ obtained from the backtranslation needs to be well-typed when linked with $\src{\library_{\comp}}$.
For context segments of the trace $\trg{\trace}$ it is also necessary to show that the execution behaves similarily, i.e., the context obtained from the backtranslation generates trace $\src{\trace}$.
For component segments of the trace, the relatedness of states and traces follows from a compiler correctness argument.
These two arguments yield the following source execution $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\runtimetermvar}}{\src{\trace}}$.

The proof now works as follows.
Given that $\msfilterL{\trg{\trace}}=\msfilterLtms{\src{\trace}}$, the proof goal changes from $\msfilterL{\trg{\trace}}\in\pi$ to $\msfilterLtms{\src{\trace}}\in\pi$.
Then, by specializing the robust satisfaction assumption $\rsat{\src{\library_{\comp}}}{\pi}$ to use the context $\src{\library_{\ctx}}$ obtained from the backtranslation which yields
 % the context segments of the target trace $\trg{\trace}$, and the 
the following source execution $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\runtimetermvar}}{\src{\trace}}$.
This gives $\msfilterLtms{\src{\trace}}\in\pi$, which was the proof goal.

>>>>

So far, the paper explained how to relate an $\Ltms$ execution with a $\Ltrg$ execution.
The next question is therefore how to build the corresponding $\Ltms$ execution.
This is done using a standard secure compilation proof technique called trace-based backtranslation~\cite{abate2019jour,korashy2021capableptrs,patrignani2021rsc}, which can be used to build a context $\src{\library_{\ctx}}$ that behaves similar to $\trg{\library_{\ctx}}$.
% Since $\Ltms$ is statically typed, the context $\src{\library_{\ctx}}$ obtained from the backtranslation needs to be well-typed when linked with $\src{\library_{\comp}}$.
For context segments of the trace $\trg{\trace}$ it is also necessary to show that the execution behaves similarily, i.e., the context obtained from the backtranslation generates trace $\src{\trace}$.
For component segments of the trace, the relatedness of states and traces follows from a compiler correctness argument.
These two arguments yield the source execution $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\runtimetermvar}}{\src{\trace}}$.

The proof now works as follows.
Given that $\msfilterL{\trg{\trace}}=\msfilterLtms{\src{\trace}}$, the proof goal changes from $\msfilterL{\trg{\trace}}\in\pi$ to $\msfilterLtms{\src{\trace}}\in\pi$.
This follows by specializing the robust satisfaction assumption $\rsat{\src{\library_{\comp}}}{\pi}$ to use the context $\src{\library_{\ctx}}$, which is obtained from the backtranslation, and to use the source execution $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\runtimetermvar}}{\src{\trace}}$.
